---
title: "The Preston Curve Revisited"
author: "Joachim Gassen"
institute: "TRR 266 Accounting for Transparency"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  beamer_presentation: 
    latex_engine: xelatex # pdflatex creates rastered fonts
    slide_level: 3

        
header-includes:
- \usepackage{booktabs} 
- \usepackage{threeparttable}
- \usepackage{graphicx}
---


```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_chunk$set(
  cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE
)
library(tidyverse)
library(kableExtra)
load("../output/results.rda")
load("../data/generated/sample.rda")
```


# Motivation

### The Preston Curve

\begin{center}
\includegraphics[width=0.8\textwidth]{../media/preston_1975_p235.png} \\
Preston (1975, p. 235)
\end{center}


### Data

```{r tab_descriptives_sample, results="asis"}
desc_rnames <- paste0("\\textit{", smp_def$label[7:9], "}")
t <- tab_desc_stat
rownames(t$df) <- desc_rnames
names(t$df)[c(5,7)] <- c("25 \\%", "75 \\%")
kable(
  t$df, digits = c(0, 3, 3, 3, 3, 3, 3, 3), format = "latex",
  caption = "\\label{tab:descriptives}Descriptive Statistics",
  format.args = list(decimal.mark = ".", big.mark = ",", 
                     scientific=FALSE),
  booktabs = TRUE, escape = FALSE, linesep = ""
) -> kab_latex

lat_tab <- unlist(strsplit(kab_latex, "\n"))
lat_tab[6] <- "\\\\[-1.8ex]\\hline \\hline \\\\[-1.8ex]"
lat_tab[8] <- "\\hline\\\\[-1.8ex]"
lat_tab[length(lat_tab) - 2] <- "\\\\[-1.8ex]\\hline \\hline \\\\[-1.8ex]"

latex_tab <- c(
  "\\begin{table}[!htbp]",  
  "\\resizebox{\\textwidth}{!}{",
  "\\begin{threeparttable}",
  lat_tab[5:(length(lat_tab) - 2)],
  "\\end{tabular}",
  "\\begin{tablenotes}[flushleft]",
  "\\setlength{\\labelsep}{0pt}",
  sprintf(
    "\\item Note: The data is obtained from the World Bank. The sample covers %d countries and the period %d to %d. \\textit{National Income per captia} values are in constant 2010 thousand U.S. dollars.", length(unique(smp$country)),
    min(as.numeric(as.character(smp$year))), 
    max(as.numeric(as.character(smp$year)))
  ),
 "\\end{tablenotes}",
  "\\end{threeparttable}",
  "}",
  "\\end{table}"
)
cat(paste(latex_tab, collapse = "\n"))  
```


### Life Expectancy by National Income

```{r Scatter}
fig_scatter
```


### No presentation without correlation table...

``` {r CorrTable, results="asis"}
tab <- tab_corr
lat_tab <- unlist(strsplit(tab$kable_ret, "\n"))
lat_tab[7:9] <- str_replace(
  lat_tab[7:9], fixed(smp_def$var_name[8:10]), smp_def$label[8:10]
)
lat_tab[4] <- "\\\\[-1.8ex]\\hline \\hline \\\\[-1.8ex]"
lat_tab[6] <- "\\hline\\\\[-1.8ex]"
lat_tab[10] <- "\\\\[-1.8ex]\\hline \\hline \\\\[-1.8ex]"
latex_tab <- c(
  "\\begin{center}",
  "\\begin{tabular}{lccc}",
  lat_tab[4:10],
  "\\end{tabular}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```


### ... and regression table

``` {r RegTable, results="asis"}
tab <- tab_regression$table
tab[12] <- paste(
  "\\\\[-1.8ex] & \\multicolumn{4}{c}{", smp_def$label[9], "} \\\\"
)
esc_var_names <- str_replace_all(smp_def$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(10, 8)],
  label = smp_def$label[c(10, 8)]
)
for (i in c(15, 18)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}

latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lcccc}",
  tab[8:33],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```


### Conclusion

- The Preston Curve is alive and well! 
- Have fun adjusting this template to fit your research needs
- Consider contributing to its repository and promote Open Science!







